Deep Learning

### 2015-01-31 deepreview.tex
revised introduction to make it more accessible

So far, most applications of deep learning use feed-forward neural
networks, but for tasks that involve sequential inputs, such as speech
and language, it is often better to use recurrent neural
networks. These are given one element from an input 
% YB term-->element 
sequence at each time step and their recurrent internal
``hidden'' state depends on the whole history of the input
sequence. Recurrent networks are very good at predicting the next
character in text~\citep{Sutskever-et-al-ICML2011} or the next
word in a sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be
used for more complex tasks.  After reading an English sentence one
word at a time, for example, an English ``encoder'' network can be
trained so that the final state vector of its hidden units is a good
representation of the thought expressed by the sentence.  This thought
vector can then be used as the initial hidden state of (or as extra
input to)  a jointly trained French ``decoder'' network which outputs a
probability distribution for the first word of the French
translation. If a particular first word is chosen from this distribution and provided as input to the decoder network it will
then output a probability distribution for the second word of the
translation and so on until a full stop is
chosen~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to the variables
in judiciously chosen rules of inference.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  Deriving conclusions using only the form of the premises (which is
what formal logic does) is a powerful
technique that people can eventually master, but the translation
results with recurrent nets suggest that it may not be a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion~\citep{metaphors,Rogers+McClelland-book2004}.

@@

\section{Recurrent Neural Networks}

>>>>

So far, most applications of deep learning use feed-forward neural
networks, illustrated in Figure~\ref{fig:backprop-box}, which learn
to map a fixed-size input (e.g., an image) to a fixed-size output
(e.g. a probability for each one of several candidate object categories). 
They do so by successive transformations corresponding to different
layers of artificial neurons (called {\em hidden units}),
which can be interpreted as learned derived features of the raw input. However, 
for tasks that involve sequential inputs, such as speech
and language, it is often better to use recurrent neural
networks, illustrated in Figure~\ref{fig:rnn} and discussed in Section~\ref{sec:rnn}. 
Recurrent neural networks process an input sequence one element at a time,
maintaining in their hidden units a ``state vector'' that implicitly contains information
about the history all the past elements of the sequence.
Recurrent networks are very good at predicting the next
character in text~\citep{Sutskever-et-al-ICML2011} or the next
word in a sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be
used for more complex tasks.  After reading an English sentence one
word at a time, for example, an English ``encoder'' network can be
trained so that the final state vector of its hidden units is a good
representation of the thought expressed by the sentence.  This thought
vector can then be used as the initial hidden state of (or as extra
input to)  a jointly trained French ``decoder'' network which outputs a
probability distribution for the first word of the French
translation. If a particular first word is chosen 
from this distribution and provided as input to the decoder network it will
then output a probability distribution for the second word of the
translation and so on until a full stop is
chosen~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to variables
in judiciously chosen rules of inference, as was previously thought by
many early AI researchers.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  
Deriving conclusions using only the form of the premises (which is
what formal logic does) is a powerful
technique that people can eventually master, but the translation
results with recurrent neural networks suggest that it may not be a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion~\citep{metaphors,Rogers+McClelland-book2004}.

@@

\section{Recurrent Neural Networks}
\label{sec:rnn}
